---
title: "DST HOMEWORK 4"
author: "DIJONE MEHMETI"
date: "01/31/2022"
output:
  html_document:
    df_print: paged
---

```{r, setup}
knitr::opts_chunk$set(echo=TRUE)
library(mdsr)
library(tidyverse)
#  tidy=FALSE,     # display code as typed
#  size="small")   # slightly smaller font for code
```

# Section titles are here (you need one hashtags)
## Subsections have 2 hashtags
### Subsubsections have 1 hashtag

- Italics: wrap your phrase with one star (\*): I *love* making DST 234!
- Bold: wrap your phrase with two stars (\*\*): The **quiz** was awesome fun!

You can wrap `R` commands in "chunks", using the syntax below

```{r}
glimpse(mpg)
```

### Including plots

You can also embed plots, for example:

```{r}
# This is my first ggplot!
ggplot(data = mpg) +
  geom_point( aes(x=displ, y=hwy, color = class) ) 
```

Compare these two plots:
```{r}

# Plot 1
ggplot(data = mpg) +
  geom_point( aes(x=displ, y=hwy), size = 5 ) 

# Plot 2
ggplot(data = mpg) +
  geom_point( aes(x=displ, y=hwy, size = displ ) ) 

```

## YOUR TURN
Using the `mpg` data frame with `x=displ, y=hwy`, generate the following ggplots (each item is a separate plot).  You can always see the first few rows of the data frame by typing `glimpse(mpg)` at the console (as we did above), or `?mpg` for the documentation on the particular data frame.  I've included the started code from earlier that you need to then modify.


a. A plot that uses color to distinguish the class of the car.
```{r}
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy, color = class)) 
```

b. A plot that makes all the points red.
```{r}
 
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy), color = "red")
```

c. A plot that makes all the shapes to be filled triangles.
(*What would it be if the shape was just a triangle with a border?*)
```{r}
```


```{r}
ggplot(data = mpg,aes(x=displ, y=hwy)) +
  geom_point(shape = 17)
```

d. A plot that makes all the points to be 3 mm in size (that is you will need `size=3`).
```{r}
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy, size = 3)) 
```

e. A plot that makes all the points red, makes all the shapes filled triangles, and the size to be three.
```{r}
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy), color = "red", shape = 17, size = 3)
```

f. A plot that uses color to distinguish the class of the car, and makes all of the points filled squares.
```{r}
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy, color = class), shape = 15)
```

g. A plot that uses shapes to distinguish the class of the car, and color to distinguish the fuel type.
```{r}
ggplot(data = mpg ) + 
  geom_point(aes(x=displ, y=hwy, shape = class, color = hwy))
```

h. One other aesthetic for `geom_point` is `alpha`, which is transparency on a scale from 0 to 1. Can you make a ggplot that from the `mpg` data frame that incorporates the aesthetics of `alpha, color, shape, size`?
```{r}
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy, alpha = class), color = "blue", shape = 17, size = 2) 
```


