---
title: "HOMEWORK 5"
author: "Dijone Mehmeti"
date: "02/09/2022"
output:
  html_document:
    df_print: paged
---

```{r, setup}
knitr::opts_chunk$set(echo=TRUE)
library(mdsr)
library(tidyverse)
library(babynames)
library(Lahman)
glimpse(Teams)
library(nycflights13)
#  tidy=FALSE,     # display code as typed
#  size="small")   # slightly smaller font for code
```

# Section titles are here (you need one hashtags)
## Problem 1
Type your response here

a) Hint: Both rows and variables are missing from the original
a) The select function will produce the result

b) Hint: the nchar() function is used in the statement.
b) The mutate function will produce the result

c) Hint: Note the new column, which is constructed from n and prop.
c) The mutate function will produce the result

d) Hint: All the years are still there, but there are only 8 rows as opposed to the original 10 rows.\
d) The summarize function will produce the result


## Problem 2
Type your response here:

babynames %>% select(n > 100)
- this is incorrect because, the select function does not take inequality as an input value

babynames %>% select(- year)
- the code is correct, since it gives us the year as output 

babynames %>% mutate(name_length == nchar(name))
- the correct way to write it would be name_length = nchar(name) not name_length == nchar(name)

babynames %>% sex == M %>% select(-prop)
- the correct way to write it would be filter(sex == M), so sex == M should be inside the filter function

babynames %>% select(year, year, sex)
- There should be only one year inside the select function not two. 

babynames %>% group_by(n) %>% summarize(ave = mean(n))
- the code is correct

babynames %>% group_by(n > 100) %>% summarize(total = sum(n))
- the code is correct

## Problem 4

Type your response here

## Inspired by class work and hint given
 
```{r}
my_teams <- mutate(Teams, BA = H/AB, SLG = (H + 2*X2B + 3*X3B + 4*HR) / AB)

ggplot(my_teams, aes(x = SLG, y = yearID)) +
  geom_point() + geom_smooth()

ggplot(my_teams, aes(x = BA, y = yearID)) + 
  geom_point() + geom_smooth()
```
## Problem 7

Type your response here

## Inspired by class work and cheat sheet
```{r}
my_teams%>%
select(yearID, teamID, SLG)%>% arrange(desc(SLG))%>%head(5)

my_teams%>%filter(yearID %in% 1969:2022)%>%
select(yearID, teamID, SLG)%>%
  arrange(desc(SLG))%>%head(5)

```
## Problem 12

Type your response here

## Inspired by class work and textbook

What is the distribution of temperature in July, 2013? Identify any important outliers in terms of the wind_speed variable.

- The distribution of temperature in July 2013 seems to peak  around 70 - 80F, and the single outlier at around 100F is the first ever observation of the wind speed

What is the relationship between dewp and humid?

- Direct relationship, as dewp increases, humid increases

What is the relationship between precip and visib?

- Indirect relationship, as precip increases, visib decreases

```{r}
weather %>%
  filter(month == 7) %>%
  ggplot(aes(x = temp)) + geom_histogram() + 
  labs(title = "Distribution of temperature in July 2013")

```

```{r}

ggplot(weather, aes(x = dewp, y = humid))+
  geom_point(size = 2) + geom_smooth(color = "yellow") + 
  labs(title = "Relationship between Dewp vs Humid")
```

```{r}
ggplot(weather, aes(x = precip, y = visib)) + 
  geom_point(size = 2) + geom_smooth(color = "purple") +
  labs(title = "Relationship between Precip vs Visib")
```