---
title: "Homework 11"
author: "Dijona, Ridwan"
date: "March 7, 2022"
output: html_document
---

```{r, setup,include=FALSE}
knitr::opts_chunk$set(echo=TRUE,message=FALSE,warning=FALSE)
library(mdsr)
library(tidyverse)
library(lubridate)
library(ggthemes)
#  tidy=FALSE,     # display code as typed
#  size="small")   # slightly smaller font for code
```

```{r}


msp311_data_url <-"https://github.com/jmzobitz/DST234Datasets/blob/master/msp311.Rda?raw=true"

load(url(msp311_data_url))

glimpse(msp311_data)

```

### Description of the question that you explored: 

What was the most subject request that was called in? and why?

### Explanation of how your data graphic addresses the question:

Our data graphic shows how many services were requested, name of the service, and the reason why it was requested.
The most frequent service request that was called in was Vehicles and Commuting with a number of 67073.The reason for the most called in service request is Traffic Control

```{r}
msp311_data%>%
  select(REASONNAME, YEAR, SUBJECTNAME)%>%
  group_by(REASONNAME, YEAR, SUBJECTNAME)%>%
  summarize(count = sum(n()))%>%
  arrange(desc(count)) %>%
  head(10)%>%
  ggplot(aes(x = SUBJECTNAME, y = count)) + geom_bar(aes(fill = REASONNAME), stat = "identity") + 
  geom_smooth(method = "lm", se = FALSE, aes(group = YEAR, color = YEAR)) + labs(
    x = " Service Request Type",
    y = " Total Number of service request ",
    title = "Most Frequent Requests Called In"

  )+ theme_wsj(base_size = 6.7, color = "brown", base_family = "sans", title_family = "mono" )+theme(
   plot.title = element_text(vjust = 2.5, color = "Brown", size = 15),
   axis.title.x =  element_text(size = 13, color = "Brown",face = "bold"),
      axis.title.y =  element_text(size = 13, color = "Brown", face = "bold"),

                             )+coord_flip()

  
  #geom_bar(aes(fill = REASONNAME), stat = "identity") 
  #geom_point(aes(color = REASONNAME))
  
```
