---
title: "HOMEWORK10"
author: "Dijona, Ly, Ridwan"
date; "March 7, 2022"
output: html_document
---


```{r cars}
summary(cars)

library(tidyverse)
library(broom)
library(mdsr)

```

Problem 1

From Chapter 25 from R for Data Science, list 2 or 3 things you learned that you can carry forward into modeling and linear regression.

The main things I have learned from this chapter are:

- You can create list-columns using mutate() and vectorized functions that return a list and summarize().
- Gapminder data summarizes the progression of countries over time, looking at statistics like life expectancy or GDP.
- I liked the description of nested data frame thinking about it as instead of repeating an action for each variable, we want to repeat an action for each country, or a subset of rows. 

Problem 2

Use the mpg dataset from to reproduce this plot:

```{r}

mpg %>%
  ggplot(aes(x = displ, y= hwy, color = as.factor(class))) +
  geom_point() + geom_smooth(method = "lm", se = FALSE)

```

Problem 3

From Question 2, use the broom package to obtain values for the slope of the different regression lines. Then create a visualization for the different slope values, adding a layer that signifies which slopes are statistically significant (p < .05 and p < .01).

```{r}
df1 <- mpg %>%
  group_by(class) %>%
  nest() 

df1$class

df1$data

df1$data[[1]]

df2 <- df1 %>%
  mutate(lmfit = map(.x=data,
                     .f=~lm(hwy~displ, data = .x)
                     ))

df3 <- df2 %>%
  mutate(tidy_vals = map(.x=lmfit,.f=tidy)
         )%>%glimpse()

 df3 %>%
  select(class,tidy_vals) %>%  
  unnest(cols = c(tidy_vals))%>%filter(term == "displ")%>%
  
  ggplot(aes(x =class, y=estimate, fill =p.value))+geom_bar(stat = "identity")+geom_smooth(method = "lm", se = FALSE)+theme_igray()+labs(x = "Type of Car", y = "Slope Values", title = "Different Slope Values for Different Type of Car Displacements")

```

```{r}
df1 <- mpg %>%
  group_by(class) %>%
  nest() 

df1$class

df1$data

df1$data[[1]]

df2 <- df1 %>%
  mutate(lmfit = map(.x=data,
                     .f=~lm(hwy~displ, data = .x)
                     ))

df3 <- df2 %>%
  mutate(tidy_vals = map(.x=lmfit,.f=tidy)
         )

fitted_coefficients <- df3 %>%
  select(class,tidy_vals) %>%  
  unnest(cols = c(tidy_vals))%>%glimpse()

x<-fitted_coefficients%>%filter(term == "displ", p.value < .05 & p.value < .01)%>%
ggplot(aes(x =term, y=estimate))+geom_bar(aes(fill = class),stat = "identity", add = "jitter")+
  geom_smooth(method = "lm", se = FALSE)


```