---
title: "HOMEWORK 3"
author: "Dijone Mehmeti"
date: "01/31/2022"
output:
  html_document:
    df_print: paged
---

```{r, setup}
knitr::opts_chunk$set(echo=TRUE)
library(mdsr)
library(tidyverse)
#  tidy=FALSE,     # display code as typed
#  size="small")   # slightly smaller font for code
```

# Section titles are here (you need one hashtags)
## Problem 1

## Submitted as a document file

Type your response here, embedding code chunks
```{r}
glimpse(mpg)
```

## Problem 2
Type your response here
#Submitted in a Document file

## Problem 3
# 5 What’s wrong with this statement?
help(NHANES, package <- "NHANES")
# The problem with the statement is that the title and the package name inside the help command need to be different

# 6 Consult the documentation for CPS85 in the mosaicData package to determine the meaning of CPS.
# The meaning of CPS is the Current Population Survey (CPS) that is used to supplement census information between census years. 

#9 A user has typed the following commands into the RStudio console.
a <- c(10, 15)
b <- c(TRUE, FALSE)
c <- c("happy", "sad")

# What do each of the following commands return? Describe the class of the object as well as its value.

#data.frame(a, b, c) # string values, Boolean
   a     b     c
1 10  TRUE happy
2 15 FALSE   sad

#cbind(a, b) ## combine columns, integer
      a b
[1,] 10 1
[2,] 15 0

#rbind(a, b) ## combine rows, integer
  [,1] [,2]
a   10   15
b    1    0

#cbind(a, b, c) ## combine columns, integer, string, boolean values

     a    b       c      
[1,] "10" "TRUE"  "happy"
[2,] "15" "FALSE" "sad" 

#list(a, b, c)[[2]] ## put them into a list, boolean

[1]  TRUE FALSE

#Problem 4 

## YOUR TURN
Using the `mpg` data frame with `x=displ, y=hwy`, generate the following ggplots (each item is a separate plot).  You can always see the first few rows of the data frame by typing `glimpse(mpg)` at the console (as we did above), or `?mpg` for the documentation on the particular data frame.  I've included the started code from earlier that you need to then modify.


a. A plot that uses color to distinguish the class of the car.
```{r}
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy, color = class)) 
```
b. A plot that makes all the points red.
```{r}
 
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy), color = "red")
```
c. A plot that makes all the shapes to be filled triangles.
(*What would it be if the shape was just a triangle with a border?*)
```{r}
```


```{r}
ggplot(data = mpg,aes(x=displ, y=hwy)) +
  geom_point(shape = 17)
```

d. A plot that makes all the points to be 3 mm in size (that is you will need `size=3`).
```{r}
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy, size = 3)) 
```

e. A plot that makes all the points red, makes all the shapes filled triangles, and the size to be three.
```{r}
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy), color = "red", shape = 17, size = 3)
```


f. A plot that uses color to distinguish the class of the car, and makes all of the points filled squares.
```{r}
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy, color = class), shape = 15)
```

g. A plot that uses shapes to distinguish the class of the car, and color to distinguish the fuel type.
```{r}
ggplot(data = mpg ) + 
  geom_point(aes(x=displ, y=hwy, shape = class, color = hwy))
```

h. One other aesthetic for `geom_point` is `alpha`, which is transparency on a scale from 0 to 1. Can you make a ggplot that from the `mpg` data frame that incorporates the aesthetics of `alpha, color, shape, size`?
```{r}
ggplot(data = mpg ) + 
  geom_point( aes(x=displ, y=hwy, alpha = class), color = "blue", shape = 17, size = 2) 
```



# Problem 5



```{r}

library(mdsr)
library(tidyverse)

memorization_data <- read_csv("C:/Users/dijon/Desktop/DST234/memorization_data.csv")

a <- ggplot(data = memorization_data, aes(y = Round, x = Gender)) +
  geom_boxplot(outlier.color  = "red", outlier.shape = 17, outlier.size = 1.5)

b <- ggplot(data = memorization_data) + 
  geom_point(aes(x = Gender, y = Round), shape = 17, color = "blue", size = 2) +
  facet_grid( Gender ~ Round )
  
c <- ggplot(data = memorization_data, aes(y = Words, x = Languages)) + 
  geom_point(aes(x = Languages, y = Words), shape = 15, color = "red", size = 1.5) +
facet_grid(Languages ~ Words )

```


```
