---
title: "HOMEWORK14"
author: "Dijone Mehmeti"
date: "4/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(mosaicData)

```

# Problem 1
- Explain what variables contained in this dataset

This dataset contain these variables:
- age is for the subject age at baseline, 
- anysub is for anysub use of any substance post-detox: a factor with levels no yes
- cesd is for Epidemiologic Studies Depression measure at baseline 
- d1 is for the lifetime number of hospitalizations for medical problems
- daysanysub is for day time to first use of any substance post-detox
- dayslink is for day time to linkage to primary care
- drugrisk is for Risk Assessment Battery drug risk scale at baseline
- e2b is for the number of times in past 6 months entered a detox program 
- female is when 0 for male, 1 for female
- sex is for a factor with levels male or female
- g1b is for experienced serious thoughts of suicide in last 30 days with a factor with levels no yes
- homeless is for housing status with a factor with levels housed homeless
- i1 is for average number of drinks consumed per day, in the past 30 days 
- i2 is for maximum number of drinks  consumed per day, in the past 30 days 
- id is for subject identifier
- indtot is for Inventory of Drug Use Consequences total score 
- linkstatus is for post-detox linkage to primary care (0 = no, 1 = yes)
- link is for post-detox linkage to primary care with no or yes
- mcs is for SF-36 Mental Component Score (measured at baseline, lower scores indicate worse status)
- pcs is for SF-36 Physical Component Score (measured at baseline, lower scores indicate worse status)
- pss_fr is for perceived social support by friends (measured at baseline, higher scores indicate more support)
- racegrp is for race/ethnicity: levels black hispanic other white
- satreat is for any BSAS substance abuse treatment at baseline: no yes
- sexrisk is for Risk Assessment Battery sex risk score (measured at baseline)
- substance is for primary substance of abuse: alcohol cocaine heroin
- treat is for randomized to HELP clinic: no yes
- hospitalizations is for lifetime number of hospitalizations for medical problems (measured at baseline)

```{r}

?mosaicData::HELPrct
mosaicData::HELPrct %>% glimpse()

```
- Run the following commands and explain what the output means:
- is.numeric() checks if it can interpreted as numbers. it outputs True for max_drinks because all the values are numbers(int) and false for treat  because the values cannot interpreted as numbers since they're strings


```{r}
is.numeric(mosaicData::HELPrct$treat)
FALSE
is.numeric(mosaicData::HELPrct$max_drinks)
TRUE

```
- Use the HELPrct data from the mosaicData to calculate the mean of all numeric variables (be sure to exclude missing values).

```{r}

HELPrct.numcols%>%
  apply(MARGIN=2, FUN = mean)


````
#Problem 2


```{r}
data_nest <- mosaicData::HELPrct %>% select(substance,age, cesd) %>%
  group_by(substance) %>%
  nest() 
  
data_nest %>% mutate(lm_fit = map(data,~lm(cesd ~ age,data=.x )), lm_summary = map(lm_fit,~broom::tidy(.x))) %>%
  select(substance,lm_summary) %>%
  unnest()

```